---
title: "Manipal Call center Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(flexdashboard)
library(readxl)
library(dplyr)
library(ggplot2)
library(reshape2)
library(plotly)
library(wordcloud)
library(tm)
comb_leads = read_xlsx("E:/Manipal/Data Visualization/Data Set/Case Study/Combined_source_wise_leads_addmission.xlsx",sheet = 1)
df = comb_leads[-c(30,31,32),c(1,2,3)]
df = df %>% mutate(not_enrolled = Lead.count-Enroll_count)
df = df %>% mutate(per_not_enrolled = not_enrolled/Lead.count*100)
df = df %>% mutate(per_enrolled = Enroll_count/Lead.count*100)
df = df %>% mutate(neg_not_enrolled = -1*not_enrolled)
a = df %>% arrange(-Enroll_count) %>% head(10)
rev = read_xlsx("E:/Manipal/Data Visualization/Data Set/Case Study/final_revenue.xlsx",sheet = 1)
combinedleads = read_xlsx("E:/Manipal/Data Visualization/Data Set/Case Study/fullcombinedleads.xlsx",sheet = 1)
p = read.csv("E:/Manipal/Data Visualization/Data Set/Case Study/leadStatus.csv")
sub = read.csv("E:/Manipal/Data Visualization/Data Set/Case Study/sub.csv")
quaterly_lead = read.csv("E:/Manipal/Data Visualization/Data Set/Case Study/quaterly_lead.csv")
quaterly_lead1 <- quaterly_lead %>% group_by(`Assigned.To`) %>% summarise(count = n(), course_count = length(unique(Course))) %>% arrange(-count) %>% head(10)
combinedleads$zz<-as.Date(combinedleads$`Callback/Followup Date`) - as.Date(combinedleads$`Recent Enquired Date`)
newdf<-combinedleads%>%group_by(`Assigned To`)%>%select(zz,Status)
newdf<-na.omit(newdf)
newdf2<-newdf%>%group_by(`Assigned To`)%>%summarise(zmean=round(mean(zz),2))
```

Enrollment 
=============================

Column {.tabset}
-----------------------------------------------------------------------

### Source wise enrollment count

```{r fig.width=10,fig.height=6}
f1 = ggplot()+geom_bar(data = a,aes(x = reorder(Source.Name,-Enroll_count),y = Enroll_count,fill = I("green")),stat = "identity")+ geom_bar(data = a,aes(x = reorder(Source.Name,neg_not_enrolled),y = neg_not_enrolled,fill = I("red"),width = 0.5),stat = "identity")+theme_bw()+geom_text(data = a,aes(x = reorder(Source.Name,-Enroll_count),y = Enroll_count,label = Enroll_count),position = position_stack(vjust = 1.5))+geom_text(data = a,aes(x = reorder(Source.Name,neg_not_enrolled),y = neg_not_enrolled,label = not_enrolled),position = position_stack(vjust = 0.5))
f2 = f1+theme(axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y = element_blank())
f3 = f2+labs(x = "Source",title = "Divergent Bar plot " ,subtitle = "Number of enrolled and not enrolled source wise")
f3

```

### Percentage of enrollment

```{r fig.width=10,fig.height=6}
le<-df[,c(1,5,6)]
anames = a$Source.Name

meltd<-melt(le)

m = meltd %>% filter(Source.Name %in% anames)
ggplot(m,aes(Source.Name,value,fill=variable))+geom_bar(stat='identity',position='fill')+ theme(axis.text.x = element_text(angle = 90))+ 
  geom_text(aes(label=value),hjust=10,vjust=0,position='fill')+coord_flip()

```


UTM source {data-navmenu="Revenue" data-orientation=rows}
=============================================================

Row
-----------------------------------------------------------------------

### Highest Revenue

```{r}

high = sub %>%arrange(-revenue) %>%  head(1)
valueBox(high,icon = "far fa-money-bill-alt",color = "green")
```


### Lowest Revenue

```{r}
low = sub %>%arrange(revenue) %>%  head(1)

valueBox(low,icon = "far fa-money-bill-alt",color = "red")
```

Row
-----------------------------

### Revenue generated with respect to each UTM source
```{r}
names(sub)[2]="Revenue"
sub$UTM.Source = tolower(sub$UTM.Source)
wordcloud(words = sub$UTM.Source,freq = sub$Revenue, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```



80-20 rule {data-navmenu="Revenue"}
====================================

Column
------------------------------------

### Number of students getting enrolled for different courses and the amount of revenue

```{r fig.width=10,fig.height=6}

t1<-rev %>% filter(admission>0 & rev$Description=="Payment Transaction Success.") %>% group_by(`Course Title`) %>% summarise(counts=n(), Revenue=sum(Amount)) %>% arrange(-Revenue)

t1$Cfreq=cumsum(t1$Revenue*100/sum(t1$Revenue))

ggplot(t1,aes(x=reorder(`Course Title`,Cfreq),fill=I('steel blue')))+ geom_bar(aes(y =Cfreq),stat = 'identity')+ 
  xlab('COURSE NAMES')+ylab("Percent Contribution to total Revenue") +
  geom_hline(yintercept = 80, linetype="dashed", color = "red")+coord_flip()+
  theme_bw()+labs(title = "Pareto Chart",subtitle = "20% of the courses contributing to 80% of revenue")


```



Orders failed {data-navmenu="Revenue"}
===========================

Column
---------------------------------------------

### Total Orders failed per Councelor

```{r fig.width=10,fig.height=6}

tt<-rev %>% filter(admission>0 & (rev$Description=="Payment Transaction Failure." |rev$Description=="Payment Transaction Pending." |rev$Description=="Payment Transaction Canceled.")) %>% group_by(`Counselor Name`) %>% summarise(counts=n()) %>% arrange(-counts)


ggplot(tt,aes(x = reorder(`Counselor Name`,counts),y = counts))+geom_point()+geom_segment(aes(x = `Counselor Name`,xend = `Counselor Name`,y = 0,yend = counts))+coord_flip()+geom_text(aes(label = counts),hjust=-0.5)+theme_bw()+theme(axis.title.x = element_blank(),axis.text.x = element_blank(),axis.ticks.x = element_blank())+labs(x = "Counselor Name",title = "Lolipop Plot",subtitle ="Counselor for whom most of orders are getting failed")

```

Revenue and Call {data-navmenu="Revenue"}
===========================

Column
----------------------------------------------------

### Revenue and Call made by top 10 Counselors

```{r}

t<-rev %>% filter(admission>0 & rev$Description=="Payment Transaction Success.") %>%  group_by(`Counselor Name`) %>% summarise(counts=n(), Revenue=sum(Amount)) %>% arrange(-Revenue) %>% head(10)

names(t)[2]="No. of Calls"
ggplotly(ggplot(t,aes(x = `No. of Calls`, y =Revenue ,col = `Counselor Name` ))+geom_point(aes(size = Revenue)))


```


Stratagy 1 {data-navmenu="Work force Stratagy"}
=====================================

Column
-------------------------------------

### Office timings

```{r fig.width=10,fig.height=6}

test=as.POSIXct(combinedleads$`Recent Enquired Date`)
combinedleads$hour=strftime(test, format="%H")

ggplot(combinedleads) + aes(x = hour) + geom_bar(fill='steelblue') +xlab("Hours of the Day")+ ylab("Count of Incoming Queries") +theme_bw() + ggtitle("Office Timings")

```


Stratagy 2 {data-navmenu="Work force Stratagy"}
=====================================

Column
-------------------------------------

### Best days to take in leave applications

```{r fig.width=10,fig.height=6}

combinedleads$Weekday <- weekdays(as.Date(combinedleads$`Assigned On`, '%d/%m/%Y'))

ggplot(combinedleads) + aes(x = Weekday) +   geom_bar(aes(fill = Weekday), width = .6) + ylab("Count of Incoming queries") +theme_bw() + ggtitle("Frequency of Calls in the Weekdays")+ theme(legend.position="none") + theme(axis.title.x=element_blank())

```




Stratagy 3 {data-navmenu="Work force Stratagy" data-orientation=rows}
=====================================

Row
-------------------------------------

### Admission Taken
```{r}

valueBox(p[1,2],icon = "fa fa-phone",color = "red")
```



### Already Applied
```{r}

valueBox(p[2,2],icon = "fa fa-phone",color = "maroon")
```

Row
-------------------------------------
```{r}

leadPlot = read_xlsx("E:/Manipal/Data Visualization/Data Set/Case Study/New_imputed.xlsx",sheet = 1)

lead = data.frame(leadPlot)

lead1 = lead %>% select(Course,Phone,City,Status) %>% filter(Status %in% c("Already Applied","Admission Taken")) %>% group_by(Course,Phone,City)

New_lead = data.frame(lead1)

df = New_lead

df_lead = data.frame(lapply(df, function(v) {
  if (is.character(v)) return(toupper(v))
  else return(v)
}))


data1 = df_lead %>% group_by(City) %>% summarise(count = n()) %>% arrange(-count) %>% head(10)

ggplot(data1,aes(x = reorder(City,count),y=count,fill = I("steel blue"))) + geom_bar(stat = 'identity')+coord_flip()+theme_bw()+geom_text(aes(label=count),hjust=5)+labs(x = "City",y = "Student count")+theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())

USPersonalExpenditure <- data.frame("Categorie" = rownames(USPersonalExpenditure), USPersonalExpenditure)
data <- USPersonalExpenditure[, c('Categorie', 'X1960')]

data <- data1[, c('City', 'count')]

colors <- c('rgb(211,94,96)', 'rgb(128,133,133)', 'rgb(144,103,167)', 'rgb(171,104,87)', 'rgb(114,147,203)')

p <- plot_ly(data, labels = ~City, values = ~count, type = 'pie',
             textposition = 'inside',
             textinfo = 'label+percent',
             insidetextfont = list(color = '#FFFFFF'),
             hoverinfo = 'text',
             text = ~paste('#', count,"Student count"),
             marker = list(colors = colors,
                           line = list(color = '#FFFFFF', width = 1)),
             #The 'pull' attribute can also be used to create space between the sectors
             showlegend = FALSE) %>%
  layout(title = 'Top Ten City Based on Addmission',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

p

```


Stratagy 4 {data-navmenu="Work force Stratagy"}
=====================================

Column
-------------------------------------

###Unique courses versus total course

```{r}
ggplotly(ggplot(quaterly_lead1,aes(x = course_count, y = count,col = Assigned.To))+geom_point(aes(size = count))+labs(x = "Unique Courses", y = "Total course count")+theme(legend.title = element_blank()))
```


Stratagy 5 {data-navmenu="Work force Stratagy"}
=====================================

Column
-------------------------------------

### Average response time for Call Back 

```{r fig.width=10,fig.height=6}

ggplot(newdf2) + geom_bar(stat = "identity" ,aes(x = newdf2$`Assigned To`, y = zmean, fill = zmean >0&zmean<5))+ theme_bw()+ ylab("Average No.Days for Response") + xlab("Employee")+ ggtitle("Average response time by employee for Callbacks and Interested Candidates") + coord_flip()+ theme(legend.position = "none")

```



